---
title: "HW4"
author: "Chris Porter"
date: "Saturday, October 01, 2016"
output: pdf_document
---

## 1. Create the Vectors:
### a) (1,2,3,...,19,20)
I'll use the combine (c) generic funtion to combine the list from 1 to 20.
```{r}
a1 <- c(1:20)
a1
```
### b) (20,19,...,2,1)
I'll use the combine (c) generic funtion to combine the list from 20 to 1.
```{r}
b1 <- c(20:1)
b1
```
### c) (1,2,3,...,19,20,19,18,...,2,1)
I'll use the combine (c) generic funtion to combine the list from 1 to 20 and another list from 19 to 1.
```{r}
c1 <- c(1:20,19:1)
c1
```
### d) (4,6,3) and assign it to the name tmp
I 'll use the combine ('c') generic function to combine a list of 4,6 and 3.
```{r}
tmp <- c(4,6,3)
tmp
```
### e) (4,6,3,4,6,3,...,4,6,3) where there are 10 occurences of 4.
I'll use the rep function to repeat the vector tmp ten times
```{r}
e1 <- rep(tmp,10)
e1
```
### f) (4,6,3,4,6,3,...,4,6,3,4) where there are 11 occurences of 4, 10 occurrences of 6 and 10 occurrences of 3.
I'll use the rep function to repeat the vector tmp ten times, and then add a 4 to the end of the vector
```{r}
f1 <- c(rep(tmp,10),4)
f1
```
### g) (4,4,...,4,6,6,...,6,3,3,...,3) where there are 10 occurrences of 4, 20 occurrences of 6 and 30 occurrences of 3.
I'll use 3 instances of the rep function in conjunction with the combine function to create this vector.
```{r}
g1 <- c(rep(4,10),rep(6,20),rep(3,30))
g1
```
## 2. Create a vector of the values of $e^x$cos(x) at x = 3,3.1,3.2,...,5.9,6.
I'll use the sequence function to create a vector of values from 3 to 6 in increments of one tenth.  Then define a function to calculate the product of the exponent and the cosine
```{r}
x <- seq(3,6,.1)
x
eXcosX <- function(x) exp(x) * cos(x)
eXcosX(x)
```
## 3. Create the following vectors: 
### a) ($0.1^30.2^1$,$0.1^60.2^4$,$0.1^90.2^7$,...,$0.1^{36}0.2^{34}$)
I'll use the repeat function to create vectors of 1 tenth and 2 tenths, and then use the sequence function to create vectors from 3 to 36 and 1 to 34 by 3, then calculate the product of the two exponent vaules using the correct combination of our 4 vectors, all of length 12.
```{r}
tenth <- rep(0.1, 12)
twentieth <- rep(0.2,12)
expA <- seq(3,36,3)
expB <- seq(1,34,3)
a3<- tenth^expA*twentieth^expB
a3
```
### b) (2,$\frac{2^2}{2},\frac{2^3}{3},...,\frac{2^25}{25}$)
I'll create two vectors, one consisting of 2's and another consisting of the series from 1 to 25, by increments of 1.  Then use the element wise exponentiation and division to calculate the vector asked in the question.
```{r}
numerator <- rep(2,25)
expDenom <- seq(1,25,1)
b3 <- numerator^expDenom/expDenom
b3
```
## 4. Calculate the following:
### a) $\sum_{i=10}^{100} (i^3 + 4i^2)$
Create a vector from 10 to 100 by 1, and a function which adds the cube and the square  of twice our independent variable
```{r}
i <- seq(10,100,1)
i
cubeQuadSquare <- function(x) (x^3 + 4*x^2)
x <- cubeQuadSquare(i)
print(sum(cubeQuadSquare(seq(10,100,1))))
print(sum(x))
```
### b) $\sum_{i=1}^{25} (\frac{2^i}{i} + \frac{3^i}{i^2})$
I'll define the function above in r, then calculate the sum from 1 to 25, by 1, and print the result
```{r}
func4b <- function(x) ((2^x/x)+(3^x/x^2))
print(sum(func4b(seq(1,25,1))))
```
## 5. Use the function paste to create the following character vectors of length 30:
###a) ("label 1", "label 2", ..., "label 30"). Note that there is a single space between label and the number following.
I'll use paste to combine the text 'Label' with a list from 1 to 30, separated by a space.
```{r}
a5 <- paste("Label", c(1:30), sep=" ")
a5
```
### b) ("fn1", "fn2", ..., "fn30"). In this case, there is no space between fn and the number following.
I'll use paste to combine the text 'fn' with a list from 1 to 30, separated by no space.
```{r}
b5<- paste("fn",c(1:30),sep="")
b5
```
## 6. Execute the following lines which create two vectors of random integers which are chosen with replacement from the integers 0,1,...,999. Both vectors have length 250.
```
set.seed(50)
xVec <- sample(0:999, 250, replace=T)
yVec <- sample(0:999, 250, replace=T)
```
```{R}
set.seed(50)
xVec <- sample(0:999, 250, replace=T)
yVec <- sample(0:999, 250, replace=T)
```
Suppose x=(x1,x2,...,xn) denotes the vector xVec and y=(y1,y2,...,yn) denotes the vector yVec.

### a)Create the vector ($y_2 - x_1,...,y_n - x_{n-1}$)
I create two new vectors of the same length, but one is the xVec from 1 to n-1, and the other is the yVec from 2 to n, Then I will use element-wise subtraction to create the new vector.
```{r}
x <- xVec[1:length(xVec)-1]
y <- yVec[2:length(yVec)]
a6 <- y-x
a6
```
### b) Create the vector ($\frac{sin(y_1)}{cos(x_2)},\frac{sin(y_2)}{cos(x_3)},...,\frac{sin(y_{n-1})}{cos(x_n)}$)
I create two new vectors of the same length, but one is the yVec from 1 to n-1, and the other is the Vec from 2 to n, Then I will use element-wise division on the sin of y divided by the cosine of x to create the new vector.
```{r}
y <- yVec[1:length(yVec)-1]
x <- xVec[2:length(xVec)]
b6 <- sin(y) / cos(x)
b6
```
### c) Create the vector ($x_1 + 2x_2 - x_3, ..., x_{n-2} + 2x_{n-1} - x_n$)
I create three new vectors of the same length, but one is the xVec from 2 to n-1 multiplied by 2, and the other is the xVec from 1 to n-2, and the third is the xVec from 3 to n. Then I will use element-wise addition and subtraction to calculate the new vector
```{r}
x1 <- xVec[1:(length(xVec)-2)] 
x2 <- 2 * xVec[2:(length(xVec)-1)] 
x3 <- xVec[3:length(xVec)]
c6 <- x1 + x2 - x3
c6
```
### d)Calculate $\sum_{i=1}^{n-1}\frac{e^{-x_{i+1}}}{x_i+10}$
Create two new x vectors of the same length, but where one is offset from the other by one element. Then calculate the above for each element in the vector, and sum all the elements.
```{r}
x1 <- xVec[1:length(xVec)-1]
x2 <- xVec[2:length(xVec)]
d6 <- sum(exp(-x2) / (x1 + 10))
d6
```
## 7. This question uses the vectors xVec and yVec created in the previous question and the functions sort, order, mean, sqrt, sum and abs.
### a) Pick out the values in yVec which are > 600
Create a boolean vector using yVec>600, then use this vector as an index to create a vector only with elements from yVec which exceed 600.
```{r}
a7 <- yVec[yVec>600]
a7
```
### b) What are the index positions in yVec of the values which >600?
Use the resulting vector from the previous questions and the match function to get the index values in yVec which exceed 600
```{r}
b7 <- match(a7,yVec)
b7
```
### c) What are the values in xVec which corrspond to the values in yVec which are > 600? 
Using the index positions from the previous question, but on the xVec.
```{r}
c7 <- xVec[b7]
c7
```
### d) Create the vector($|x_1-\bar{x}|^{1/2}, |x_2-\bar{x}|^{1/2}, ...,|x_n-\bar{x}|^{1/2}$) where $\bar{x}$ denotes the mean of the vector x = ($x_1, x_2, ...,x_n$)
Use the abs and mean function on the x vector to calculate the above.
```{r}
d7 <- abs( xVec - mean(xVec) )^(1/2)
d7
```
### e)How many values in yVec are within 200 of the maximum value of the terms in yVec?
Create a boolean vector with the above condition being TRUE (or =1), then sum this vector.
```{r}
e7 <- sum(yVec>=(max(yVec)-200))
e7
```
### f) How many number in xVec are divisble by 2?
Similar to g, but the condition uses the modulo to determine if it is divisible by 2.
```{r}
evens <- sum(xVec %% 2)
evens
```
### g) Sort the numbers in the vector xVec in the order of increasing values in yVec
Use the sort function to sort the y vector, use the match function to determine it's location in the original yVec, and then use this index to arrange the xVec.
```{r}
sortY <- sort(yVec)
ySortIndex <- match(sortY,yVec)
sortX <- xVec[ySortIndex]
sortX
```
### h) Pick out the elements in yVec at index positions 1,4,7,10,13,...
Create a sequence from 1 to 250 in increments of 3, and use this to index the yVec
```{r}
x <- seq(1,250,3)
h7 <- yVec[x]
h7
```
## 8. By using the function cumprod or otherwise, calculate: $1 + \frac{2}{3} + \frac{(2*4)}{(3*5)} + \frac{(2*4*6)}{(3*5*7)}+...+\frac{(2*4*...*38)}{(3*5*...*39)}$
Use the cuumulative product to calculate the numerators and denominators in the above sequence, then sum it and add 1.
```{r}
numerator <- cumprod(seq(2,38,2))
denominator <- cumprod(seq(3,39,2))
numerator
denominator
answer <- 1 + (numerator / denominator)
answer
```